---
title: "Is Boulder a bike-friendly tourist city? "
author: "Zhongyi Zhang"
date: "2021/10/31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Boulder

The City of Boulder is a home rule municipality that is the county seat and most populous municipality of Boulder County, Colorado, United States.Boulder is located at the base of the foothills of the Rocky Mountains, at an elevation of 5,430 feet (1,655 m) above sea level. Boulder is 25 miles (40 km) northwest of the Colorado State Capitol in Denver. 

It's a beautiful city with many nature landmarks and there are always some hikers and cyclists along the streets.

So I want to examine the basic geographic information (including *elevation* and *bike lanes*), distance to natural landmarks, and compare the distance from biking trails and social media photographs, to find out is Boulder a bike-friendly tourist city.


## Data and packages

```{r}
library(ggplot2)
library(sf)
library(tidyverse)
library(ggspatial)
library(viridis)
```

At first, we need some packages for the geovisualizations. Use `library()` function to intialize them.

Then we should grab some data [here](https://drive.google.com/drive/folders/1YuX5oWjKS6vZx4zNyPwBKuiw9EJYNX5L?usp=sharing) from Google drive. And import the data as a sf spatial dataset.

```{r}
boulder <- st_read("~/adv lab1/drive-download-20211031T042259Z-001/BoulderSocialMedia.shp")
boulder
```

This Here are the details of data: 

|  Variable  |  Description   |
|------------|-----------------------------------------------------------------------------------|
| DB |  indicates whether the point is a   social media location (Flickr or Panramio) or a point in the park |
| NatMrk_Dis |  distance to natural landmark |
| Bike_dis |  distance to biking trails |
| PT_Elev |  Elevation |


## Basic geographic information

We need to choose an appropriate projection.

```{r}
boulder = st_transform(boulder, 26753) 
```

We can use the `ggplot2` to plot the elevation data and grab the base map of bike lanes from the [OpenStreetMap](https://www.openstreetmap.org/search?query=boulder#map=12/40.0294/-105.2398).

```{r}
ggplot() +
  annotation_map_tile(type = "http://toolserver.org/tiles/hikebike/${z}/${x}/${y}.png") +
  geom_sf(data = boulder, aes(color=PT_Elev),
          fill = NA, alpha = .1) + 
  scale_colour_gradientn(colours = magma(10))
```

As we can see from the map, the west part of the mountain is higher than the east part. And the bike lanes is very dense in the city. It's a **good** city for cyclists.
There are many other 


## The distance from natural landmarks

```{r}
ggplot() +
    geom_sf(data =boulder, aes(color=NatMrk_Dis),
    fill = NA, alpha = .2) +
  scale_colour_gradientn(colours = terrain.colors(10)) +  
  theme_bw()
```

There are five landmarks in the area we examined. And due to its high density, the distance from most of tourists in this area is less than 1000 meters. It's easy for the tourists to get to there within a day.


## The distance from biking trails and social media photographs

Then we can compare the distance from biking trails and social media photographs.
```{r}
boulder %>%
  filter(DB ==  'Pano' | DB == 'Flickr') %>%
  ggplot(aes(x=DB, y=Bike_dis)) + 
  geom_boxplot()
```

The middle value of the distance from biking trails to the location of social media photographs is pretty close, which is around 800 meters. The interquartile range of both is pretty similar. The data from Flickr has a much bigger range compare to the data from Pano. In conclusion, if the cyclists want to find a good location to take a photo then post on the social media, they better check the Flickr, and most of the good location is not far from the biking trails.


## Conclusion

Boulder is definitely **a bike-friendly city**, it has dense bike lanes, and many of the natural landmarks are close to each other, so people can ride a bike to get to there instead of driving a car.The setting of biking trails is relatively appropriate most of the social media picture is taken not far away from the trails.



## What are the benefits and challenges of an open data science approach? Give an example based on this week's reading. (1-2 paragraphs)

For example, the human geography and broader social science research can only seek to extract information and draw conclusions from a small numbers of observations before the big data era, but in today, so much of big data with spatial attributes can represent a huge potential opportunity for human geography.

For challenges, in human geography researchers need to develop some new methods to handle and analyse them, and they are not well-prepared for the big data now. And big data is usually generated by privately owned businesses and government.Geographers will be cut-off from a rich seam of potential studies. Even if they get the data, there are a number of ethical and security challenges of working with such data.
